---
title: "team"
author: "Zack Johnson"
date: "9/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Team question : Which company has the highest average ratings?

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

```{r}
require(tidyverse) # Data visualization

choco_highest5 <- choco %>%
  group_by(Company) %>%
  summarise(mean_rate = mean(Rating), n = n()) %>%
  arrange(desc(mean_rate)) %>%
  filter(n > 5) #filter to be above the mean of n to avoid having 
choco_highest5 <- choco_highest5[1:5,]
```


#Team question: What are some better ways we can look at the difference between types

```{r}
require(tidyverse)
require(patchwork)

#Im bringing in some of the data transformations I used in individual1.Rmd

#make a table and then only take the descriptors that have more than 55 for Characteristics1 
char1_table <- table(choco$Characteristics1)
char1_table <- char1_table[char1_table > 55]
char1_most <- names(char1_table)
choco_char1 <- choco %>%
  filter(Characteristics1 %in% char1_most)
#do the same thing for Characteristics2
char2_table <- table(choco$Characteristics2)
char2_table <- char2_table[char2_table > 55]
char2_most <- names(char1_table)
choco_char2 <- choco %>%
  filter(Characteristics2 %in% char2_most)

#save box plots that are segmented by characteristic in question
char1_box <- ggplot(data = choco_char1, aes(Rating, x = Characteristics1))+ 
  geom_boxplot()
char2_box <- ggplot(data = choco_char2, aes(Rating, x = Characteristics2))+ 
  geom_boxplot()

#plot the two together
plot(patchworkGrob(char1_box / char2_box))

#conduct a t test between creamy and all others
t.test(choco_char1$Rating[choco_char1$Characteristics1 == "creamy"], choco_char1$Rating[choco_char1$Characteristics1 != "creamy"])
```
In this, in all likelihood, better look at the difference between characteristics, there are more clear some things that show up in more positive reviews. The word "creamy" has a mean for characteristic 1 that is at 3.5 that is statistically significantly different than all the others.
#Team Question: Among the top 4 of national cocoa locations of origin, is there significant difference between Ratings
```{r}
require(tidyverse)

#similar method of using table and names to extract the most frequent country of origin
origin_table <- table(choco$Bean_Origin)
origin_table <- origin_table[origin_table > 200]
origin_most <- names(origin_table)
choco_origin <- choco %>%
  filter(choco$Bean_Origin %in% origin_most)

#plot the box plots for each country
ggplot(data = choco_origin, aes(Rating, x = Bean_Origin)) +
  geom_boxplot()
```

Among these 4 top producing countries there is no statistical difference between the means of scores.
